Long groovy title goes here

### 2013-07-10 shanghai.tex
Working on converting xy to tikz

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Short groovy title goes here]{Long groovy title goes here}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{manfnt}

@@

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Weil}{W}
\newcommand{\Frob}{{\operatorname{Fr}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}

@@

%\input{introduction}
%In his celebrated thesis, John Tate writes 
%\begin{quotation}
%    {\it Concerning the characters of $k^*$ [the
%    multiplicative group of a $\mathfrak{p}$-adic field], the
%    situation is different from that of $k^+$.  First of all, we are
%    interested in continuous multiplicative maps $\alpha \mapsto
%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
%    bounded ones, and shall call such a map a quasi-character,
%    reserving the word ``character'' for the conventional character of
%    absolute value $1$. Secondly, we shall find no model for the group
%    of quasi-characters, or even for the group of characters, though
%    such a model would be of the utmost importance.}
%  \cite{Tate:thesis}*{\S 2.3}
%\end{quotation}
%\noindent
In this paper we show that the monidal category of character sheaves
on the Greenberg transform of the locally finite type Neron model of
$T$ provides an elegant, canonical model for the group of
(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
field and $T$ is any algebraic torus over $K$.

@@

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  \Clifton{Agreed. I'll do that.}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

\Clifton{I'm going to remove all mention of line bundles from this paper.}

@@

  Observe that $\bm: \bG\times \bG\to \bG$ is
  completely determined by the family of maps
  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
  for all $x,y\in X$. To do that, note first that the local system
  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
  \[
  \xymatrix{
    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
    }
  \]
  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
  the result is the middle horizontal diagram below, where we use the
  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
  \[
  \xymatrix{
    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
    && \ar@{=}[u] \bG^x\times \bG^y\\
    }
  \]
  Now, the homomorphism from the covering group of
  $\bf^x\times\bf^y$ to the covering group of
  $\bf^{x+y}$ induced by the composition
  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
  Since this map commutes with the characters $\psi_x\otimes\psi_y$
  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
  It is straightforward (but laborious) to show that the pair
  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.

@@

\begin{remark}
  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
  a smooth group scheme and if all geometric automorphisms of $f$ are
  fixed by Frobenius, then every character of $\ker f$ determines a
  character sheaf on $G$. However, it is not true that every character
  sheaf on $G$ arises in this manner.
\end{remark}
\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
%\input{centralextensions}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
  \]
\end{theorem}

@@

\Clifton{Explain what happens as $d$ varies.}
Suppose $d\leq d'$.

@@

\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
  care about \ref{scheme}.}

\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
 of our definitions, above.}

\begin{proposition}
  Fundamental properties of $\GN{T}$:
  \begin{enumerate}
  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
  \end{enumerate}
\end{proposition}

@@

\section{Functorial properties of the main isomorphism}

We have already seen that the trace of Frobenius defines a canonical isomorphism 
$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we expand on the canonicity of this group isomorphism 
by showing that it is a natural transformation. We also show

\begin{proposition}
The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
is a natural transformation between the following two contravariant functors 
from the category of algebraic tori over $K$ to the category of abelian groups: 
\begin{enumerate}
\item $T \mapsto \CSiso{\GN{T}}$
\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
\end{enumerate}
\end{proposition}

\Clifton{I think I can prove this proposition without too much difficulty.}
\begin{proof}
\end{proof}

\begin{proposition}
Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
\Clifton{This next part is very much under construction.}
The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
that commutes, through trace of Frobenius, with ...
\[
\xymatrix{
\CS(\GN{T}) \ar[d] & \CSiso{\GN{T}} \ar[r]^{t_T} \ar[d] & \Hom_\text{ad}(T(K),\EEx) \ar[d] \\
\CS(\GN{T}') & \CSiso{\GN{T}'} \ar[r]^{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)\\
}
\]
\end{proposition}

\begin{proof}
\end{proof}

>>>>

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Short groovy title goes here]{Long groovy title goes here}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc}
\usepackage{manfnt}

@@

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Weil}{W}
\newcommand{\Frob}{{\operatorname{Fr}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}

@@

%\input{introduction}
In his celebrated thesis, John Tate writes 
\begin{quotation}
    {\it Concerning the characters of $k^*$ [the
    multiplicative group of a $\mathfrak{p}$-adic field], the
    situation is different from that of $k^+$.  First of all, we are
    interested in continuous multiplicative maps $\alpha \mapsto
    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
    bounded ones, and shall call such a map a quasi-character,
    reserving the word ``character'' for the conventional character of
    absolute value $1$. Secondly, we shall find no model for the group
    of quasi-characters, or even for the group of characters, though
    such a model would be of the utmost importance.}
  \cite{Tate:thesis}*{\S 2.3}
\end{quotation}
\noindent
In this paper we show that the monidal category of character sheaves
on the Greenberg transform of the locally finite type Neron model of
$T$ provides an elegant, canonical model for the group of
(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
field and $T$ is any algebraic torus over $K$.

@@

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

@@

  Observe that $\bm: \bG\times \bG\to \bG$ is
  completely determined by the family of maps
  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
  for all $x,y\in X$. To do that, note first that the local system
  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
  \[
  \xymatrix{
    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
    }
  \]
  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
  the result is the middle horizontal diagram below, where we use the
  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.

  \vspace{0.2in}

  \begin{tikzpicture}[style={rectangle, scale=1.2}]
  \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
  \node (22) [anchor=west] at (4.4,2) {$\bH^{x+y}$};
  \node (32) [anchor=east] at (11,2) {$\bG^{x+y}$};
  \node (01) at (0,1) {$\EEx$};
  \node (11) [anchor=east] at (4,1) {$\Aut(\bf^{x+y})$};
  \node (21) [anchor=west] at (4.4,1) {$\bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y$};
  \node (31) [anchor=east] at (11,1) {$\bG^x\times \bG^y$};
  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
  \node (20) [anchor=west] at (4.4,0) {$\bG^x\times \bG^y$};
  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
  \draw [->] (4.3,1.94) arc (330:30:0.12);
  \draw [->, densely dotted] (4.3,0.94) arc (330:30:0.12);
  \draw [->] (4.3,-0.06) arc (330:30:0.12);
  \draw [->] (12) -- (01);
  \draw [->, densely dotted] (11) -- (01);
  \draw [->] (10) -- (01);
  \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
  \draw [double equal sign distance] (11) -- (12);
  \draw [->] (22) -- (32);
  \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
  \draw [->] (21) -- (31);
  \draw [->] ($(32.south) + (0,-0.5)$) -- (32);
  \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
  \draw [->] (20) -- (30);
  \draw [->] ($(32.south) + (0,-1.5)$) -- ($(32.south) + (0,-1)$);
  \end{tikzpicture}

  \[
  \xymatrix{
    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
    && \ar@{=}[u] \bG^x\times \bG^y\\
    }
  \]
  Now, the homomorphism from the covering group of
  $\bf^x\times\bf^y$ to the covering group of
  $\bf^{x+y}$ induced by the composition
  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
  Since this map commutes with the characters $\psi_x\otimes\psi_y$
  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
  It is straightforward (but laborious) to show that the pair
  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.

@@

\begin{remark}
  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
  a smooth group scheme and if all geometric automorphisms of $f$ are
  fixed by Frobenius, then every character of $\ker f$ determines a
  character sheaf on $G$. However, it is not true that every character
  sheaf on $G$, in the sense of Section~\ref{sec:category} arises not
  all character sheaves on $G$ arise in this manner.
\end{remark}
%\input{centralextensions}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
  \]
\end{theorem}

@@

\Clifton{Explain what happens as $d\in \NN$ varies.}
Suppose $d\leq d'$.

@@

\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
  care about \ref{scheme}.}
\begin{proposition}
  Fundamental properties of $\GN{T}$:
  \begin{enumerate}
  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
  \end{enumerate}
\end{proposition}

@@
